### 2020-03-20 README.Rmd
trying to get run_cv to work

# ID which points are in buffer and which are not
buffer_index <- st_intersects(scbi_growth_df, scbi_buffer, sparse = FALSE)
scbi_growth_df <- scbi_growth_df %>% 
  mutate(buffer = as.vector(buffer_index))

@@

* CV: `run_cv()` is a wrapper to `fit_bayesian_model()` and `predict_bayesian_model()`.

```{r}

>>>>

# ID which points are in buffer and which are not
buffer_index <- !st_intersects(scbi_growth_df, scbi_buffer, sparse = FALSE)
scbi_growth_df <- scbi_growth_df %>% 
  mutate(buffer = as.vector(buffer_index))

@@

For the above results we fit the model to the entire data set, and then make predictions across the entire data set from that fit. This could lead to overfitting because we are using the training data to also test the model. If model error is spatially correlated this could be a large issue (cite important sources here!). We can use the spatial block structure we defined above to deal with with. The function `run_cv` goes through each fold in the `cv_grid` and fits the model on all the other folds. Then applies that fit to the focal fold. It is a wrapper for `fit_bayesain_model` and `predict_bayesain_model` but fits a seperate model for each fold.

```{r}
scbi_cv_predict <- focal_vs_comp_scbi %>%
  run_cv(model_specs = scbi_specs, max_dist = max_dist, cv_grid = scbi_cv_grid)
